---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scatterwithoutlier

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of scatterwithoutlier is to create scatterplot for two quantitative variables with labeled outliers. This function takes a dataset(as a list, and dataframes/tibbles are lists) of two quantitative variables and fits a single linear regression model from them, then it displays a scatterplot with fitted regression line. Also, it displays any influential points as red color based on user defined criteria (cut-off for cook’s distance).


## Development Process

Overall, this package was developed using the modern functions usethis() and devtools(), with some manual edits. Specifically:

usethis or devtools functions applied:

  - create_package("scatterwithoutlier") and use_git() applied to generate the local package.
  - use_r("scatterwithoutlier") generated scatterwithoutlier.R in the R folder.
  - use_testthat() generated the tests folder and associated files.
  - use_test("scatterwithoutlier") generated test-scatterwithoutlier.R in tests folder.
  - use_package("dplyr") generated the dependecy on package "dplyr".
  - use_pipe() generated the dependecy on package "magrittr".
  - use_package("gapminder") generated the dependecy on package "gapminder".
  - use_package("stats") generated the dependecy on package "stats".
  - use_readme_rmd() generated README.Rmd.
  - build_readme() generated README.md from README.Rmd.
  - use_vignette("scatterwithoutlier") generated vignettes.
  - build_vignettes() built the vignettes.
  - use_mit_license("Tianyi Zheng") generated LICENSE.md.
  - use_code_of_conduct() generated CODE_OF_CONDUCT.md.
  - usethis::use_pkgdown() and pkgdown::build_site() generated the package website.

Manual works:

  - manually created a project on Github website, and pushed the local package into the repo.
  - manually implemented scatterwithoutlier.R and test-scatterwithoutlier.R based on Assignment 1.
  - manually filled in information for Readme, and vignettes.
  - manually created and filled in information for NEWS.md.
  - manually added a badge.

Also, tests are developed to validate the function is outputing a ggplot object, and raising an error upon unexpected inputs.

## Installation

`scatterwithoutlier` is not on CRAN yet, so the best way to install it is:

``` r
# install.packages("devtools")
devtools::install_github("tianyica/scatterwithoutlier")
```

## Example


```{r example}
library(scatterwithoutlier)
```

The following example plots the relationship between life expectancy (as independent variable) and population (as dependent variable) from the gapminder dataset on the default settings.

```{r }
scatterwithoutlier(gapminder::gapminder %>%
     dplyr::select(lifeExp,pop))
```

The following example plots the relationship between life expectancy (as independent variable) and population (as dependent variable) from the gapminder dataset on the threshold of 0.05 on cook's distance, and outputing the message on the count of influential observations and the process of the function.

```{r }
scatterwithoutlier(gapminder::gapminder %>%
     dplyr::select(pop,lifeExp),xy=FALSE,cooksd=0.05,verbose = TRUE,outputcount = TRUE)
```

The following example plots the relationship between life expectancy (as independent variable) and GDP per capita (as dependent variable) from the gapminder dataset on the threshold of 0.05 on cook's distance.

```{r }
scatterwithoutlier(gapminder::gapminder %>%
     dplyr::select(lifeExp,gdpPercap),cooksd = 0.05)
```

